Competing Bandits:\\ The Perils of Exploration under Competition \thanks{This is an extended abstract of \citet{CompetingBandits-merged}, which in turn subsumes conference papers \citet{CompetingBandits-itcs18} and \citet{CompetingBandits-ec19}.}

### 2020-12-20 journal paper/content/related_work.tex
Minor edit to give credit to Che-Horner.

The three-way tradeoff between exploration, exploitation and incentives has been studied in mechanism design, in several scenarios very different from ours:
incentivizing exploration in a recommendation system
(starting from \citet{Kremer-JPE14}, see \citet[Ch. 11.6]{slivkins-MABbook} for a literature review),
    %\citep[\eg][]{Che-13,Frazier-ec14,Kremer-JPE14,ICexploration-ec15,Bimpikis-exploration-ms17,Bahar-ec16,Jieming-unbiased18},
dynamic auctions
    (\eg see \citet{DynAuctions-survey10} for a survey),
    %\citep[\eg][]{AtheySegal-econometrica13,DynPivot-econometrica10,Kakade-pivot-or13},
pay-per-click ad auctions
    \citep[\eg][]{MechMAB-ec09,DevanurK09,Transform-ec10-jacm},
coordinating search and matching
    \citep{Bobby-Glen-ec16},
and human computation
    \citep[\eg][]{RepeatedPA-ec14,Ghosh-itcs13,Krause-www13}.
%A literature review of this work can be found in
%\citep[Ch. 11.6]{slivkins-MABbook}.

>>>>

The three-way tradeoff between exploration, exploitation and incentives has been studied in (algorithmic) mechanism design, in several scenarios very different from ours. In particular: 
incentivized exploration in a recommendation system
(starting from \citet{Kremer-JPE14,Che-13}, see \citet[Ch. 11.6]{slivkins-MABbook} for a literature review),
    %\citep[\eg][]{Che-13,Frazier-ec14,Kremer-JPE14,ICexploration-ec15,Bimpikis-exploration-ms17,Bahar-ec16,Jieming-unbiased18},
dynamic auctions
    (\eg see \citet{DynAuctions-survey10} for a survey),
    %\citep[\eg][]{AtheySegal-econometrica13,DynPivot-econometrica10,Kakade-pivot-or13},
pay-per-click ad auctions
    \citep[\eg][]{MechMAB-ec09,DevanurK09,Transform-ec10-jacm},
coordinating search and matching
    \citep{Bobby-Glen-ec16},
and human computation
    \citep[\eg][]{RepeatedPA-ec14,Ghosh-itcs13,Krause-www13}.
%A literature review of this work can be found in
%\citep[Ch. 11.6]{slivkins-MABbook}.
